% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{center}
\textbf{\Large Yunke Li}
\end{center}
\begin{tabular*}{7in}{l@{\extracolsep{3.7in}}l}
1175 Mcgowan Dr.& \hfill Cell:\ 250-552-0039 \\
Prince George, BC V2M 6S4 & \hfill Email:\ cboy2332@hotmail.com \\
\end{tabular*}
\\
\begin{center}
\textbf{\Large Post-graduate in Computer Science}
\end{center}

\vspace{0.1in}

\resheading{Highlights of Qualifications}
\begin{itemize}
\item{Python: 3 years experience at school, home, and work.}
\item{Java: 4 years experience at school, home.}
\item{PHP/HTML/CSS/MySQL: 5 years website development experience at school and work.}
\item{Proficient in Ubuntu, have used it for 4 years for developing and building web server.}
\item{CUDA: 3 years experience at research.}
\item{Data Analysis: 4 years experience at research dealing face datasets.}
\item{C/electronic engineer: 3 years experience at school for MCU development and robot competition (last used in 2013).}
\item{C\#/.NET Framework 4: 1 years study at home.}
\end{itemize}


\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of Northern British Columbia}{Prince George, BC}{MSc in Computer Science}{Sep. 2013 - Apr. 2018}
	\begin{itemize}
		\resitem{Thesis: "Face Recognition using Convolutional Macropixel Comparison Approach"}
		\resitem{Paper: "Face Recognition Using Convolutional Macropixel Approach" accepted by IEEE ICCI'18}
		\resitem{Developed artificial intelligence face recognition system using deep learning framework and CUDA (parallel computing platform).}
		\resitem{Processing and Analyzing face datasets}
		\resitem{Proficient in caffe (deep learning framework) using Python and TensorFlow using Python.}
	\end{itemize}
	
\item
	\ressubheading{Tianjin University}{Tianjin, China}{Bachelor of Science in Computer Science}{Sep. 2009 - May. 2013}
	\begin{itemize}
		\resitem{Thesis: “Natural Action Recognition based on real-time template matching”}
		\resitem{Strong emphasis on website development, software development and MCU development.}
		\resitem{Project leader of the University’s website. Developed several projects including e-shop, administrative system and student community system.}
	\end{itemize}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Baidu, Inc.}{Beijing}{Web Development Intern}{Jan, 2013 - April, 2013}
	\begin{itemize}
		\resitem{Company: Baidu is one of the largest internet companies in China. It holds the 2nd largest search engine in the world and holds more than 70\% market in China.}
		\resitem{Product: Baidu Tieba (tieba.baidu.com) is the largest chinese communication platform. The platform is based on user-generated content model and supports users to creat, search or join a bar (forum) based on keyword.}
		\resitem{Duties: 3 months internship in Baidu Tieba technology department. Developing and maintaining web client of Tieba. Improved and adjusted the front-end framework mainly using html, css and javascript. Participated in developing recommendation system and Promotion-Content feature.}
	\end{itemize}
\item
	\ressubheading{Goldstream Publishing Inc.}{Prince George, BC}{Mitacs Project Research Intern Assistant}{March, 2014 - July, 2014}
	\begin{itemize}
		\resitem{Duties: web crawler development, web page development and text data organizing}
		\resitem{Products: Web Crawler and Dyyde Web Page}
		\resitem{Web Crawler: The crawler is programed using python. It connected to the main text mining application which is focusing on building an automated text mining algorithm to extract location-based information from online documents. The crawler extracts the useful information from specific websites (fishing community forums and fishing information websites) and regroups the text data format to be easily used by text mining application.}
		\resitem{Gyyde Web Page: The first version of gyyde website. It is a size automatically adjustable web page which is used for introducing the gyyde mobile application. The web could be viewed on both PC and mobile devices.}
	\end{itemize}
\item
	\ressubheading{Clean Energy Consulting Inc.}{Prince George, BC}{Mitacs Project Research Intern}{July, 2014 - November, 2014}
	\begin{itemize}
		\resitem{Duties: application design, data structure design, program development and data analyze}
		\resitem{Products: Power Plant Fuel Control And Optimization Program}
		\resitem{Power Plant Fuel Control and Optimization Program: The Mitacs project aims to develop a software providing systematic tracking and forecasting capabilities for power plant at Conifix Power facility in Mackenzie, British Columbia. The software is built as a web based application in order to support network communication. The expectation of the software is being able to predict insufficient or excess of fuel in order to help optimize fuel price, displaying graphical interfaces for viewing real time view consumption. One requirement for the programming is the accessibility to multiple parties inside and outside the plant control network.}
		\resitem{Observed and studied the Industrial Process of Power Plant, then designed the control system for it.}
	\end{itemize}
\item
	\ressubheading{University of Northern British Columbia}{Prince George, BC}{Teaching Assistant, Tutor \& Lab instructor}{April, 2014 - June, 2014}
	\begin{itemize}
		\resitem{Course: CPSC 100 - Computer Programming I}
		\resitem{An overview tutorial of computer hardware and software. Java is introduced and taught as the mai language in this course.}
		\resitem{Tutorial including programming skills, programing language features, coding standard and development process is provided.}
		\resitem{Introduction and Tutorial of Linux, editors, Java compiler and debugging tools are provided in the labs.}
	\end{itemize}
\item
	\ressubheading{University of Northern British Columbia}{Prince George, BC}{Teaching Assistant \& Lab instructor}{January, 2016 — April, 2016}
	\begin{itemize}
		\resitem{Course: CPSC 425 - Compiler Design}
		\resitem{An introduction to programming language translation, compilers, interpreters, and other language processors.}
		\resitem{Assistance and quality assessment is provided to students who are required to design and implement a compiler for a specific language.}
		\resitem{Assistant is also responsible for code assessment, compiler test, environment construction and interpreter support on Ubuntu.}
	\end{itemize}

\end{itemize}

\resheading{Interests}
\begin{itemize}
\item{Sport: Soccer, badminton.}
\item{Computing: Developing website for fun. Developed new home website for Multicultural Heritage Society of Prince George (not yet online)}
\item{Musical: Accordion}
\item{Other: Travelling, cooking, reading about history, investing and science fiction}
\end{itemize}


\end{document}
