%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{oldstyle}                           % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{8cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Yunke}{Li}
\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{1175 Mcgowan Dr}{Prince George V2M6S4}{Canada}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~2505520039}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{cboy2332@hotmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Information and Technology Services}{Department of International Education\\College of New Caledonia\\3330 22 Ave\\Prince George}
\date{May 9, 2018}
\opening{Dear officer of AxiomZen,}
\closing{Yours faithfully,}
\makelettertitle

I am writing to you regarding the **** position at ****. I found your posting on **** and was instantly attracted to the opportunities offered by this job. ****'s reputation for responsive service and proactive support differentiates your company from the rest, and I would like to be part of your dynamic team.

I am a conscientious and high-achieving Master of Computer Science degree holder majoring in Artificial Intelligence. I have exceptional technical and analytical skills, with experience in software development, web development, database management, network and server support, program configuration, testing and evaluation, algorithm design, data analysis, which I have gained in study/research and various programmer roles. 

I first started my IT related working experience back at Tianjin University as the project leader of the university's website studio which is the top class university web studio in China. Then I was recommended by the studio to enter Baidu Inc., which is one of the largest internet companies in China, as intern programmer. Experiences in Baidu were invaluable in allowing me to open my eyes to the creative challenges required in the industry and develop/apply my skills in a professional context. I rapidly adapted to the new work culture and team members who became trusted associates throughout my time spent there.

In Canada during the graduate study, I have gained further experience aside from my research, through the Mitacs internship program for Clean Energy Consulting Inc. and Goldstream Publishing Inc. in Prince George. One of them is developing a text mining application which is an automated text mining algorithm to extract location-based information from online documents. Another is an automatic inventory control system used by heat power station to monitor and predict the transport and inventory status of fuel.

You will find me to be a positive, motivated, and hard-working person who is keen to learn and contribute. My technical skills are combined with excellent communication skills that allow me to work effectively and positively and get along well with others.

I am eager to pursue a successful career in IT, and the **** position is perfectly aligned with my skills and interests. I believe that I have the right skills and experience to be a great fit for this position. My resume is attached and I look forward to being able to discuss the position with you further.


\makeletterclosing

\end{document}


%% end of file `template.tex'.
